Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 evaluation.tex
Add discussion of overhead target vs. overhead seen.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring.
With a 2x overhead target, UMC achieves 22\% monitoring coverage on average and with a 4x overhead target, this increases to 49\%.
%We see that
%with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
%By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
%average. 
Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With only a 1.01x overhead, LS achieves 30\% coverage on average. This increases to
71\% coverage with a 1.1x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.

>>>>

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring.
With a 2x overhead target, UMC achieves 22\% monitoring coverage on average and with a 4x overhead target, this increases to 49\%.
%We see that
%with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
%By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
%average. 
Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With only a 1.01x overhead, LS achieves 30\% coverage on average. This increases to
71\% coverage with a 1.1x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.
Note that the overheads shown are the target overhead. In some cases, a high
overhead target is needed in order to achieve 100\% coverage. For example, for
{\tt mcf} with UMC monitoring, a 12x overhead target is needed to achieve 100\%
coverage while the overheads of performing monitoring in full were 2.6x (see
Figure~\ref{fig:evaluation.filtering}. This is due to the fact that we
accumulate slack gradually and so bursty monitoring events may require a higher
overhead target in order for all monitoring to be performed. However, the
actual overheads seen are in-line with the overhead of performing monitoring
without dropping (e.g., 2.6x for {\tt mcf} with UMC monitoring at a 12x
overhead target).
